Hydra Battles and Cie

### 2021-09-02 doc/part-hydras.tex
Corrections in chapter 4
Simplification of old latex snippets

    \vspace{4pt}
    \emph{From Module~\href{../theories/html/hydras.Epsilon0.Hessenberg.html\#oplus}{Epsilon0.Hessenberg}}

@@

    A first set of lemmas correspond to the various cases of \texttt{oplus}'s 
    definition. They can be proved almost immediately.

    \input{movies/snippets/Hessenberg/oplusNeutral}

@@

    We prove  the commutativity of $\oplus$ in two steps.

    First, we prove by transfinite induction on $\alpha$ that the restriction of $\oplus$ to the
    interval $[0..\alpha)$ is commutative.

@@

    \input{movies/snippets/Hydra_Termination/mNf}

@@

\subsubsection{Limit ordinals are truly limits}
The following theorem states that any limit ordinal $\lambda<\epsilon_0$ 
is the limit of the sequence \showmath{\canonseq{\lambda}{i}\;(1\le i)}.

@@

\begin{Coqsrc}
 path_to omega (2::2::2::nil) (omega * 2).

 path_to omega (3::4::5::6::nil) (omega * 2).

 path_to zero (interval 3 14) (omega * 2).

 path_to zero (repeat 3 8) (omega * 2).
\end{Coqsrc}

>>>>

  \pagebreak 
  \vspace{4pt}
    \emph{From Module~\href{../theories/html/hydras.Epsilon0.Hessenberg.html\#oplus}{Epsilon0.Hessenberg}}

@@

    A first set of lemmas correspond to the various cases of \texttt{oplus}'s 
    definition. They can be proved almost immediately. Here are a few examples.

    \inputsnippets{Hessenberg/oplusNeutral,
      Hessenberg/oplusCompareLt}

@@

    We prove  the commutativity of $\oplus$ in two steps. 
    First, we prove by transfinite induction on $\alpha$ that the restriction of $\oplus$ to the
    interval $[0..\alpha)$ is commutative.

@@

    \input{movies/snippets/Hydra_Termination/mNf}
      \input{movies/snippets/Hydra_Termination/msNf}

@@

\subsubsection{Limit ordinals are truly limits}
The following theorem states that any limit ordinal $\lambda<\epsilon_0$ 
is the limit of the sequence $\canonseq{\lambda}{i}\;(1\le i)$.

@@

\inputsnippets{Paths/exPathTac} 
\end{exercise}
